Supplemental Information B: Power Simulations

### 2023-08-17 PathModels.Rmd
path model adj

coreNeedPathS1 <-
  data.frame(
    lab_x_direct = "Core Need\\\\Fulfillment",
    lab_y_direct   = "Outgroup\\\\Attitudes",
    lab_x   = "Core Need\\\\Fulfillment",
    lab_m   = "Interaction\\\\Quality",
    lab_y   = "Outgroup\\\\Attitudes",
    coef_xy_direct = pathCoeffs$Study1$xy_direct,
    coef_xm = pathCoeffs$Study1$xm,
    coef_my = pathCoeffs$Study1$my,
    coef_xy = pathCoeffs$Study1$xy,
    fig_num = "A",
    study_num = "Study 1:"
  )
coreNeedPathS2 <-
  data.frame(
    lab_x_direct = "Core Need\\\\Fulfillment",
    lab_y_direct   = "Outgroup\\\\Attitudes",
    lab_x   = "Core Need\\\\Fulfillment",
    lab_m   = "Interaction\\\\Quality",
    lab_y   = "Outgroup\\\\Attitudes",
    coef_xy_direct = pathCoeffs$Study2$xy_direct,
    coef_xm = pathCoeffs$Study2$xm,
    coef_my = pathCoeffs$Study2$my,
    coef_xy = pathCoeffs$Study2$xy,
    fig_num = "B",
    study_num = "Study 2:"
  )
coreNeedPathS3 <-
  data.frame(
    lab_x_direct = "Core Need\\\\Fulfillment",
    lab_y_direct   = "Outgroup\\\\Attitudes",
    lab_x   = "Core Need\\\\Fulfillment",
    lab_m   = "Interaction\\\\Quality",
    lab_y   = "Outgroup\\\\Attitudes",
    coef_xy_direct = pathCoeffs$Study3$xy_direct,
    coef_xm = pathCoeffs$Study3$xm,
    coef_my = pathCoeffs$Study3$my,
    coef_xy = pathCoeffs$Study3$xy,
    fig_num = "C",
    study_num = "Study 3:"
  )

>>>>

coreNeedPathS1 <-
  data.frame(
    lab_x_direct = "Sit. Need\\\\Fulfillment",
    lab_y_direct   = "Outgroup\\\\Attitudes",
    lab_x   = "Sit. Need\\\\Fulfillment",
    lab_m   = "Interaction\\\\Quality",
    lab_y   = "Outgroup\\\\Attitudes",
    coef_xy_direct = pathCoeffs$Study1$xy_direct,
    coef_xm = pathCoeffs$Study1$xm,
    coef_my = pathCoeffs$Study1$my,
    coef_xy = pathCoeffs$Study1$xy,
    fig_num = "A",
    study_num = "Study 1:"
  )
coreNeedPathS2 <-
  data.frame(
    lab_x_direct = "Sit. Need\\\\Fulfillment",
    lab_y_direct   = "Outgroup\\\\Attitudes",
    lab_x   = "Sit. Need\\\\Fulfillment",
    lab_m   = "Interaction\\\\Quality",
    lab_y   = "Outgroup\\\\Attitudes",
    coef_xy_direct = pathCoeffs$Study2$xy_direct,
    coef_xm = pathCoeffs$Study2$xm,
    coef_my = pathCoeffs$Study2$my,
    coef_xy = pathCoeffs$Study2$xy,
    fig_num = "B",
    study_num = "Study 2:"
  )
coreNeedPathS3 <-
  data.frame(
    lab_x_direct = "Sit. Need\\\\Fulfillment",
    lab_y_direct   = "Outgroup\\\\Attitudes",
    lab_x   = "Sit. Need\\\\Fulfillment",
    lab_m   = "Interaction\\\\Quality",
    lab_y   = "Outgroup\\\\Attitudes",
    coef_xy_direct = pathCoeffs$Study3$xy_direct,
    coef_xm = pathCoeffs$Study3$xm,
    coef_my = pathCoeffs$Study3$my,
    coef_xy = pathCoeffs$Study3$xy,
    fig_num = "C",
    study_num = "Study 3:"
  )
